---
title: "BGR Pull"
author: "Jake Dubbert"
date: "February 18, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The following code scrapes the desired PDFs from the BGR website, https://www.bgr.bund.de/EN/Themen/Energie/energie_node_en.html,and exports them to an excel file for the following IFs variables:

EnCumProdGasBGR: uses table Natural Gas in XXXX (year), column Cum. Production 
EnCumProdOilBGR: uses table Crude Oil in XXXX (year), column Cum. Production 
EnReserCBMBGR: Coalbed Methane Reserves. Table Natural Gas Resources (under CBM) 
EnReserGasBGR: Uses table Natural Gas in XXXX (Year), Column: Reserves 
EnReserHeavyOilBGR: Uses table Crude Oil Reserves, Extra Heavy Oil column 
EnReserOilBGR: Utilizes table Crude Oil in XXXX (year), column Reserves 
EnReserOilSandsBGR: Uses table Crude Oil Reserves, column Oil Sand 
EnReserShaleGasBGR: Uses table Natural Gas Reserves, column Shale Gas 
EnReserShaleOilBGR: Uses table Crude Oil Reserves, column Shale Oil 
EnResorCBMBGR: Uses table Natural Gas Resources, column CBM 
EnResorGasBGR: Uses table Natural Gas in XXXX (year), column Remaining Potential 
EnResorHeavyOilBGR: Uses table Crude Oil Resources, column Extra Heavy Oil 
EnResorOilBGR: Uses table Crude Oil in XXXX (year), column Remaining Potential 
EnResorOilSandsBGR: table Crude Oil Resources, column Oil Sand 
EnResorShaleGasBGR: table Natural Gas Resources in XXXX, Column Shale Gas 
EnResorShaleOilBGR: table Crude Oil Resources, Column Shale Oil 
EnResorTightGasBGR: table Natural Gas Resources, column Tight Gas

Press CONTROL+ALT+R to run the entire script


Packages need to run the script
```{r}
library(tabulizer)
library(rJava)
library(dplyr)
library(miniUI)
library(gtools)
library(openxlsx)
library(shiny)
library(varhandle)
library(stringr)
```
 
## BGR 2016
```{r}
link <- "https://www.bgr.bund.de/EN/Themen/Energie/Downloads/energiestudie_2017_en.pdf?__blob=publicationFile&v=2"
```

## Crude Oil 2016
```{r}
aa <- extract_tables(link, encoding = "UTF-8", pages = 116:119, method = "stream")
crude_oil_2016 <- as.data.frame(do.call(rbind, aa))
crude_oil_2016 <- crude_oil_2016[-c(1:2,44:45,89:90,133:134,158:169),]
crude_oil_2016 <- crude_oil_2016[,-c(2,5:6)]
names(crude_oil_2016)[names(crude_oil_2016)=="V1"] <- "country"
names(crude_oil_2016)[names(crude_oil_2016)=="V3"] <- "EnCumProdOilBGR"
names(crude_oil_2016)[names(crude_oil_2016)=="V4"] <- "EnReserOilBGR"
names(crude_oil_2016)[names(crude_oil_2016)=="V7"] <- "EnResorOilBGR"
crude_oil_2016$year <- 2016
crude_oil_2016 <- crude_oil_2016[,c(1,5,2,3,4)]
crude_oil_2016 <- unfactor(crude_oil_2016)
crude_oil_2016[crude_oil_2016=="-"] <- 0
crude_oil_2016[crude_oil_2016=="n. s."] <- NA
```

## Natural Gas 2016
```{r}
a <- extract_tables(link, encoding = "UTF-8", pages = 126:129, method = "stream")
natgas_2016 <- as.data.frame(do.call(rbind, a))
natgas_2016 <- natgas_2016[-c(1:2,45:46,88:89,131:132,155:166),]
natgas_2016 <- natgas_2016[,-c(2,5:6)]
names(natgas_2016)[names(natgas_2016)=="V1"] <- "country"
names(natgas_2016)[names(natgas_2016)=="V3"] <- "EnCumProdGasBGR"
names(natgas_2016)[names(natgas_2016)=="V4"] <- "EnReserGasBGR"
names(natgas_2016)[names(natgas_2016)=="V7"] <- "EnResorGasBGR"
natgas_2016$year <- 2016
natgas_2016 <- natgas_2016[,c(1,5,2,3,4)]
natgas_2016 <- unfactor(natgas_2016)
natgas_2016[natgas_2016=="-"] <- 0
natgas_2016[natgas_2016=="n. s."] <- NA
```

## Crude Oil Reserves Table
```{r}
tbl1 <- extract_tables(link, encoding = "UTF-8", pages = 121)
oil_reserve_2016 <- as.data.frame(do.call(rbind, tbl1))
oil_reserve_2016 <- oil_reserve_2016[-c(1:2,23:38),]
oil_reserve_2016 <- oil_reserve_2016[,-c(1,3,4)]
names(oil_reserve_2016)[names(oil_reserve_2016)=="V2"] <- "country"
names(oil_reserve_2016)[names(oil_reserve_2016)=="V5"] <- "EnReserShaleOilBGR"
names(oil_reserve_2016)[names(oil_reserve_2016)=="V6"] <- "EnReserOilSandsBGR"
names(oil_reserve_2016)[names(oil_reserve_2016)=="V7"] <- "EnReserHeavyOilBGR"
oil_reserve_2016$year <- 2016
oil_reserve_2016 <- oil_reserve_2016[,c(1,5,2,3,4)]
oil_reserve_2016 <- unfactor(oil_reserve_2016)
oil_reserve_2016[oil_reserve_2016=="-"] <- 0
oil_reserve_2016[oil_reserve_2016=="n. s."] <- NA
```

## Crude Oil Resources Table
```{r}
tbl2 <- extract_tables(link, encoding = "UTF-8", pages = 120, method = "stream")
oil_resource_2016 <- as.data.frame(do.call(rbind, tbl2))
oil_resource_2016 <- oil_resource_2016[-c(1:2,23:38),]
oil_resource_2016 <- oil_resource_2016[,-c(1,3,4,7)]
oil_resource_2016 <- unfactor(oil_resource_2016)
oil <- str_split_fixed(oil_resource_2016$V6, " ", 2)
oil_resource_2016 <- oil_resource_2016[,-3]
oil_resource_2016 <- cbind(oil_resource_2016, oil)

names(oil_resource_2016)[names(oil_resource_2016)=="V2"] <- "country"
names(oil_resource_2016)[names(oil_resource_2016)=="V5"] <- "EnResorShaleOilBGR"
names(oil_resource_2016)[names(oil_resource_2016)=="1"] <- "EnResorOilSandsBGR"
names(oil_resource_2016)[names(oil_resource_2016)=="2"] <- "EnResorHeavyOilBGR"
oil_resource_2016$year <- 2016
oil_resource_2016 <- oil_resource_2016[,c(1,5,2,3,4)]
oil_resource_2016 <- unfactor(oil_resource_2016)
oil_resource_2016[oil_resource_2016=="-"] <- 0
oil_resource_2016[oil_resource_2016=="n. s."] <- NA
```

## Natural Gas Reserves Table
```{r}
tbl3 <- extract_tables(link, encoding = "UTF-8", pages = 131, method = "stream")
gas_reserve_2016 <- as.data.frame(do.call(rbind, tbl3))
gas_reserve_2016 <- gas_reserve_2016[-c(1:2,23:38),]
gas_reserve_2016 <- gas_reserve_2016[,-c(1,3,4)]
gas_reserve_2016 <- unfactor(gas_reserve_2016)
gas <- str_split_fixed(gas_reserve_2016$V5, " ", 2)
gas_reserve_2016 <- gas_reserve_2016[,-2]
gas_reserve_2016 <- cbind(gas_reserve_2016, gas)
gas_reserve_2016 <- as.data.frame(gas_reserve_2016)

names(gas_reserve_2016)[names(gas_reserve_2016)=="gas_reserve_2016"] <- "country"
names(gas_reserve_2016)[names(gas_reserve_2016)=="V2"] <- "EnReserShaleGasBGR"
names(gas_reserve_2016)[names(gas_reserve_2016)=="V3"] <- "EnReserCBMBGR"
gas_reserve_2016$year <- 2016
gas_reserve_2016 <- gas_reserve_2016[,c(1,4,2,3)]
gas_reserve_2016 <- unfactor(gas_reserve_2016)
gas_reserve_2016[gas_reserve_2016=="-"] <- 0
gas_reserve_2016[gas_reserve_2016=="n. s."] <- NA
```

## Natural Gas Resources Table
```{r}
tbl4 <- extract_tables(link, encoding = "UTF-8", pages = 130, method = "stream")
gas_resource_2016 <- as.data.frame(do.call(rbind, tbl4))
gas_resource_2016 <- gas_resource_2016[-c(1:2,23:38),]
gas_resource_2016 <- gas_resource_2016[,-c(1,3,4)]

names(gas_resource_2016)[names(gas_resource_2016)=="V2"] <- "country"
names(gas_resource_2016)[names(gas_resource_2016)=="V5"] <- "EnResorTightGasBGR"
names(gas_resource_2016)[names(gas_resource_2016)=="V6"] <- "EnResorShaleGasBGR"
names(gas_resource_2016)[names(gas_resource_2016)=="V7"] <- "EnResorCBMBGR"
gas_resource_2016$year <- 2016
gas_resource_2016 <- gas_resource_2016[,c(1,5,2,3,4)]
gas_resource_2016 <- unfactor(gas_resource_2016)
gas_resource_2016[gas_resource_2016=="-"] <- 0
gas_resource_2016[gas_resource_2016=="n. s."] <- NA
```

## BGR ALL 2016
```{r}
nat2 <- full_join(gas_reserve_2016, gas_resource_2016, by =c("country", "year"))
oil <- full_join(oil_reserve_2016, oil_resource_2016, by = c("country", "year"))
nat_oil <- full_join(nat2, oil, by = c("country", "year"))
nat_oil2 <- full_join(natgas_2016, crude_oil_2016, by = c("country", "year"))
bgr_2016 <- full_join(nat_oil,nat_oil2, by = c("country", "year"))
```

## Concord to country list
```{r}
concordance <- read.csv("IFS_country_concordance_BGR.csv")
bgr_2016 <- full_join(bgr_2016, concordance, by = "country")
bgr_2016 <- bgr_2016[,-1]
bgr_2016 <- bgr_2016[,c(19,1:18)]
```

```{r}
write.xlsx(bgr_2016, "bgr_2016_final.xlsx")
```

